### 2018-02-06 Paper/jaccardbaetica.tex
add morisita

This paper aims to highlight the production dynamics in relation to a specific area within Roman Empire. We explore here the economic relation between stamps and workshops.

@@

As a complement of Jaccard distance, we use the statistical technique Morisita-Horn index. Unlike Jaccard distance, this method was performed to measure the overlap between different samples of sets \citep{horn_measurement_1966}. In ecology, it describes the dissimilarity between the system of two communities.

Considering our dataset as non-uniform sample, this method provides a useful tool to handle large samples with different sizes and diversity. Index can be describe considering 0 as no presence of similarity of stamps and 1 a totally similarity between stamps.

@@

>>>>

This paper aims to highlight the production dynamics in relation to a specific area within Roman Empire. We explore here the economic relationship between stamps and production centres.

@@

As a complement of Jaccard distance, we use the statistical technique Morisita-Horn index. Unlike Jaccard distance, this method was performed to measure the overlap between different samples of sets \citep{horn_measurement_1966}. In Ecology, it describes the dissimilarity between the system of two communities.

Considering our dataset as non-uniform sample, this method provides a useful tool to handle large samples with different sizes and diversity. Morisita-Horn index can be expressed considering 0 as total presence of similarity of stamps and 1 a totally dissimilarity between stamps.

@@

\subsection{Jaccard distance}

Result of Jaccard distance can be The coefficients range from x to x.

The dendrogram shown in Fig. Bla bla was obtained with the Jaccard distance measure. The dendrogram suggests
